We demonstrated gain tunable optical analogs of Electromagnetically Induced Transparency (EIT) and Electromagnetically Induced Absorption (EIA). This allowed us to precisely control superluminal and subluminal group velocities of light in a coupled ring resonator system, with a linear gain excitation and enabled reversible transitions between them. Furthermore, we observed sub and superluminal light featuring all-optical EIT resonance, which in all previous studies, based on passive coupled ring resonators, has been observed to yield only subluminal light.

 We also studied the spectral and dispersive properties of a cascade of three mutually coupled ring resonators. We have found a number of unique cascaded resonances which display distinct spectral and dispersive behavior. Based on our inquiry, we propose new applications of coupled resonators for future quantum and optical information and communication technologies.

The optimized coupled resonators demonstrate continuous variable of sub and superluminal group velocities and can be tuned owing to excitation of linear optical gain, we can observe astounding spectral characteristics. These features of coupled resonators also allow acquiring control of transmission and photon storage times inside the optical cavity. Furthermore, cascades of ring resonators additionally enhance these characteristics and exhibit unique features such as sub and superluminal at multiple wavelengths. The findings of this thesis are of great significance for the future of photonics and optical communicating systems.